---
title: "The CLT"
author: "Laizha Grajeda De Leon"
date: "Summer 2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
require(tidyverse)
require(lattice)
```

```{r}
Homers_data <- read.csv(file="Homers_data.csv")
my1000 <- sample(Homers_data$kkardashtemp ,size = 1000, replace=T)
densityplot(my1000,main="original data")

options(digits=1)
```


Describe the resulting plot -  is it unimodal?  How many peaks does it have?  Are all the peaks the same size? 

In the graph above, it's not unimodal but in fact it is bimodal, seeing that there is only two peaks. Both peaks are no the same size. The sample mean is `r mean (my1000)` and the standard deviation is `r sd(my1000)`



Now take 2 random samples of 1000 points of the kkardashtemp variable and form 1000 points of their averages,

```{r}
numb = 2
Hdata   <- sample(Homers_data$kkardashtemp ,size = numb*1000, replace=T)
mdata  <-matrix(Hdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
densityplot(x.avg,main="sample size 2")

```

Describe the resulting plot -  is it unimodal?  How many peaks does it have?  Are all the peaks the same size? 

The resulting plot is trimodal, where there are three peaks. All three spikes are not the same size. The sample mean is `r mean (x.avg)` and the standard deviation is `r sd(x.avg)`
 

Do this again for 4 random samples

```{r}
numb = 4
Hdata   <- sample(Homers_data$kkardashtemp ,size = numb*1000, replace=T)
mdata  <-matrix(Hdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
densityplot(x.avg,main="sample size 4")

```

 The sample mean is `r mean (x.avg)` and the standard deviation is `r sd(x.avg)`

Then again for 9 random samples

```{r}
numb = 9
Hdata   <- sample(Homers_data$kkardashtemp ,size = numb*1000, replace=T)
mdata  <-matrix(Hdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
densityplot(x.avg,main="sample size 9")

```

The sample mean is `r mean (x.avg)` and the standard deviation is `r sd(x.avg)`

then 16 random samples


```{r}
numb = 16
Hdata   <- sample(Homers_data$kkardashtemp ,size = numb*1000, replace=T)
mdata  <-matrix(Hdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
densityplot(x.avg,main="sample size 16")

```

The sample mean is `r mean (x.avg)` and the standard deviation is `r sd(x.avg)`


finally for 36 random samples.

```{r}
numb = 36
Hdata   <- sample(Homers_data$kkardashtemp ,size = numb*1000, replace=T)
mdata  <-matrix(Hdata,nrow=1000,ncol=numb)
x.avg <- apply(mdata,1,mean)
densityplot(x.avg,main="sample size 36")

```


The sample mean is `r mean (x.avg)` and the standard deviation is `r sd(x.avg)`


Write a summary paragraph describing what you observed and how it relates to the central limit theorem.

When viewing all of the graphs and random sample size in each graph, there is a pattern that slowly agrees with the theory of CLT. The central limit theorem shows how the mean and standard deviation and takes samples from the graphs and or situations/questions with replacement, then shows us the distribution of the sample means which will be approximately and normally distributed.